Prefix-free graphs and suffix array construction in sublinear space

### 2023-06-21 manuscript/main.tex
added segment table

Next, for each suffix of a segment join, we need to calculate the corresponding
segment ID and the segment position.
These two arrays represent the current suffix of a segment join starts with a
particular segment and the position in this segment.
This can be computed using an inverse permutation of a suffix array of a segment
join in linear time.
To illustrate the procedure, consider the segment join of our running example in
Figure \ref{fig:ids_and_positions}.
Each position of the join can be assigned a segment ID and a position in current
segment by linearly iterating the segment join and incrementing ID and position
accordingly.
Then, applying the inverse permutation of a suffix array to these arrays will
change the order of computed values in a way corresponding to the sorted suffixes.
The Table \ref{} shows the resulting suffix array, LCP array, segment ID array and segment position array.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{images/segment_table.png}
    \caption{}
    \label{fig:segment_sa}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{images/segment_metainfo.png}
    \caption{}
    \label{fig:segment_meta}
\end{figure}

>>>>

Next, for each suffix of a segment join, we need to calculate the corresponding
segment ID and the segment position.
These two arrays represent the current suffix of a segment join starts with a
particular segment and the position in this segment.
This can be computed using an inverse permutation of a suffix array of a segment
join in linear time.
To illustrate the procedure, consider the segment join of our running example in
Figure \ref{fig:ids_and_positions}.
Each position of the join can be assigned a segment ID and a position in current
segment by linearly iterating the segment join and incrementing ID and position
accordingly.
Then, applying the inverse permutation of a suffix array to these arrays will
change the order of computed values in a way corresponding to the sorted suffixes.
The Table \ref{tab:suffix} shows the resulting suffix array, LCP array, segment ID array and segment position array.

@@

In the Table \ref{tab:suffix}, one row can represent multiple positions of the
pangenome.
In order to be able to reconstruct the suffix array, we need to store some
additional information for each segment.
For each segment, we store it's length, it's starting positions in the implicit
concatenated pangenome and the rank of it's right context.

\input{segment_table.tex}
